### 2018-10-16 manuscript.rmd
added figure 1, made palette colorblind friendly

```{r}
cteno_color = "#F8766D"
poro_color = "#00BA38"
unresolved_color = "#6F94CD"

@@

@@

@@

@@

analyses %>% 
	ggplot( aes(x=model_summary, y=taxon_sampling, col=result) ) +
		geom_jitter( width = 0.20, height = 0.20, alpha=0.7, size=2 ) +
		theme_classic()
```

@@

>>>>

```{r}

# A colorblind friendly palette from http://www.cookbook-r.com/Graphs/Colors_(ggplot2)/#a-colorblind-friendly-palette:
cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")

result_colors = c( cbPalette[2], cbPalette[4], cbPalette[1] )
names( result_colors ) = c( "Ctenophora-sister", "Porifera-sister", "Unresolved" )

@@

Casey W. Dunn^1^*, Benjamin Evans^2^, and Yuanning Li^1^

^1^Department of Ecology and Evolutionary Biology, Yale University

^2^Yale Center for Research Computing, Yale University

\* Corresponding author, casey.dunn@yale.edu

## Abstract

@@

![](figures/Figure_overview.png)
**Fig XXOverview.** (A) The Ctenophora-sister hypothesis posits that there is a clade (designated by the orange node) that includes all animals except Ctenophora, and that Ctenophora is sister to this clade. (B) The Porifera-sister hypothesis posits that there is a clade (designated by the green node) that includes all animals except Porifera, and that Porifera is sister to this clade. Testing these hypotheses requires evaluating the support for each of these alternative nodes. (C) A ctenophore. (D) A sponge.

@@

### Alignment overlap

### Support for Porifera-sister and Ctenophora-sister

@@

analyses %>% 
	ggplot( aes(x=model_summary, y=taxon_sampling, col=result) ) +
		geom_jitter( width = 0.20, height = 0.20, alpha=0.7, size=2 ) +
		scale_colour_manual(values = result_colors) +
		theme_classic()
```

@@

## New analyses of published matrices

One of the challenges of interpretting support for the placement of the animal root across studies is that different programs, sofware versions, and settings have been used across studies, and phylogenetic analysis decisions have been approached in very different ways. Here we reanalyze the primary matrices from each study under consistent conditions with iqtree. We selected this tool because it has greater model flexibility than other tools and is very fast.

We

### Comparison of iqtree and phylobayes results

## New analyses of new matrices

## The current state of understanding

## Next steps

## Conclusion

## Methods

All files associated with this analysis are available at https://github.com/caseywdunn/animal_root

### Data wrangling

### Matrix comparison and annotation

### Phylogenetic analyses

## Ackowledgements

Author contributions

\pagebreak

## Supplemental Information
